### 2020-11-02 reports/article.tex
final article, figures, notebooks (+linting)

% A set scenario LULC maps generated with increasing proportion of pixels changed to its corresponding LULC code with high tree canopy cover, its corresponding simulated air temperatuers and heat mitigation are shown in \autoref{fig:scenarios-prop} (see \ref{sec:scenarios-prop}).
% The maps for four scenarios generated by changing an increasing proportion of pixels to its corresponding LULC code with high tree canopy cover are shown in \autoref{fig:scenario-maps}.
The LULC, temperature and heat mitigation maps for the scenarios generated by transforming a 25, 50, 75 and 100\% of the candidate pixels are shown in \autoref{fig:scenario-maps}.
% \begin{figure}
%   \begin{subfigure}{\textwidth}
%     \centering
%     \includegraphics[width=\textwidth]{figures/scenarios-prop-lulc.png}
%   \end{subfigure}
%   \begin{subfigure}{\textwidth}
%     \centering    
%     \includegraphics[width=\textwidth]{figures/scenarios-prop-T.png}  
%   \end{subfigure}
%   \begin{subfigure}{\textwidth}
%     \centering    
%     \includegraphics[width=\textwidth]{figures/scenarios-prop-mitigation.png}
%   \end{subfigure}
%   \caption{\label{fig:scenarios-prop} Scenario raster maps with an increasing (from left to right) proportion of the pixels changed to its corresponding LULC code with high tree canopy cover. The rows respectively feature the pixels where the LULC is changed (top), the simulated air temperature (middle) and the simulated heat mitigation (bottom).}
% \end{figure}
\begin{figure}
  \begin{adjustwidth}{-.4\textwidth}{0cm}
    \includegraphics[width=\linewidth]{figures/scenario-lulc-maps.png}
    \includegraphics[width=\linewidth]{figures/scenario-T-maps.png}
    \includegraphics[width=\linewidth]{figures/scenario-heat-mitigation-maps.png}
    % \begin{subfigure}{\linewidth}
    %   \includegraphics[width=\textwidth]{figures/scenarios-prop-lulc.png}
    % \end{subfigure}
    % \begin{subfigure}{\linewidth}
    %   \includegraphics[width=\textwidth]{figures/scenarios-prop-T.png}  
    % \end{subfigure}
    % \begin{subfigure}{\linewidth}
    %   \includegraphics[width=\textwidth]{figures/scenarios-prop-mitigation.png}
    % \end{subfigure}
    % \captionsetup{width=\linewidth, margin={0cm,-.4\textwidth}}
    \caption{\label{fig:scenario-maps} Simulated LULC (top), temperature (middle) and heat mitigation (bottom) maps by transforming a 25, 50, 75 and 100\% of the candidate pixels to its corresponding LULC code with high tree canopy cover. The pixel values of each map are aggregated out of all the sampling approaches and simulation runs, i.e., the LULC maps show the mode, whereas the temperature and heat mitigation maps show the average. See the Jupyter Notebook at \hyperref[sec:si-scenarios]{section S2.1} for the detailed numbers of the figure.}
  \end{adjustwidth}
\end{figure}
When changing a 25, 50, 75 and 100\% of the candidate pixels, the maximum temperature $T$ for the reference date, i.e., 26.05$\degree C$, is progressively reduced to 25.77, 25.30, 24.82 and 24.49 $\degree C$ respectively, while the magnitude of maximum heat mitigation $T - T_{obs}$ increases from 0.49, 1.17, 1.81 and 2.22$\degree C$ respectively.
The largest heat mitigation magnitudes occur in the most urbanized parts, which are located along the main transportation axes.
The relationship between the proportion of candidate pixels transformed and the simulated distribution of air temperature can be approximated by a straight line with a negative slope (see \autoref{fig:si-scenario-T-regplot} and \autoref{fig:si-scenario-T-hists} for more details about this relationship).
% The strength of such a fit suggests that the constraints on the urban heat mitigation imposed by the existing urban fabric .

@@

% The differences between the spatially scattering or scattering the transformed pixels are most notable when considering the number of dwellers exposed to temperatures higher than 24$\degree$C and 25$\degree$C.
% Regarding the spatial configurations, scattering the transformed pixels instead of clustering them with other high tree canopy pixels can result in a reduction of the 3238, 9597 and 15323 dwellers exposed to temperatures higher than 24$\degree$C for the same proportions of transformed pixels of 25, 50 and 75\%, which respectively represents a 1.17, 3.47 and 5.53\% of the total number of dwellers. For temperatures higher than 25$\degree$C, the analogous reduction is of 20708 and 22748 dwellers when transforming a 25 and 50\% of the pixels, which represents a 7.48 and 8.22\% of the population.
The way in which the transformed pixels are sampled has significant effects on the human exposure to high temperatures (\autoref{fig:human-exposure-comparison}). 
\begin{figure}[ht]
  \begin{adjustwidth}{-.4\textwidth}{0cm}  
    \centering
    \includegraphics[width=\linewidth]{figures/human-exposure-comparison}
    \caption{\label{fig:human-exposure-comparison} Effect of the sampling approach on the population exposed to temperatures higher than 21, 22, 23, 24, 25 and 26$\degree$C for an overall proportion of transformed pixels of 0, 25, 50, 75 and 100\%. See the Jupyter Notebook at \hyperref[sec:si-human-exposure]{section S2.3} for the detailed numbers of the figure.}
  \end{adjustwidth}
\end{figure}
Overall, scattering the transformed pixels to avoid forming a continuous tree canopy appears as the most effective approach to reduce the human exposure to the highest temperatures, followed by random sampling.
When transforming a 25 and 50\% of the candidate pixels with the scattering approach, the number of dwellers exposed to temperatures over 25$\degree$C diminishes from 124073 to 65108 and 4498 respectively. % (which is 4.57 an 64.57\% larger than the corresponding reduction when averaged among the three approaches)
Such a reduction is larger than its random sampling counterpart by 3125 and 8223 dwellers respectively, and larger than its clustering approach counterpart by 9359 and 21388 dwellers respectively.
% which is larger than its counterpart when reduction  corresponds to  less dwellers than when transforming the same amount of pixels with random sampling approach, and 9359 and 21388.

@@

\begin{figure}[H]
  \centering
  \includegraphics[width=.98\textwidth]{figures/monitoring-stations}
  \caption{\label{fig:monitoring-stations} Locations of the monitoring stations used to get the $T_{ref}$ and $UHI_{max}$ parameters. The basemap tile is provided by StamenDesign, under CC BY 3.0, with data from OpenStreetMap, under ODbL.}
\end{figure}

>>>>

% A set scenario LULC maps generated with increasing proportion of pixels changed to its corresponding LULC code with high tree canopy cover, its corresponding simulated air temperatuers and heat mitigation are shown in \autoref{fig:scenarios-prop} (see \ref{sec:scenarios-prop}).
% The maps for four scenarios generated by changing an increasing proportion of pixels to its corresponding LULC code with high tree canopy cover are shown in \autoref{fig:scenario-maps}.
The LULC, temperature and heat mitigation maps for the scenarios generated by transforming a 25, 50, 75 and 100\% of the candidate pixels are shown in \autoref{fig:scenario-maps}.
% \begin{figure}
%   \begin{subfigure}{\textwidth}
%     \centering
%     \includegraphics[width=\textwidth]{figures/scenarios-prop-lulc.png}
%   \end{subfigure}
%   \begin{subfigure}{\textwidth}
%     \centering    
%     \includegraphics[width=\textwidth]{figures/scenarios-prop-T.png}  
%   \end{subfigure}
%   \begin{subfigure}{\textwidth}
%     \centering    
%     \includegraphics[width=\textwidth]{figures/scenarios-prop-mitigation.png}
%   \end{subfigure}
%   \caption{\label{fig:scenarios-prop} Scenario raster maps with an increasing (from left to right) proportion of the pixels changed to its corresponding LULC code with high tree canopy cover. The rows respectively feature the pixels where the LULC is changed (top), the simulated air temperature (middle) and the simulated heat mitigation (bottom).}
% \end{figure}
\begin{figure}
  \begin{adjustwidth}{-.4\textwidth}{0cm}
    \includegraphics[width=\linewidth]{figures/scenario-lulc-maps.png}
    \includegraphics[width=\linewidth]{figures/scenario-T-maps.png}
    \includegraphics[width=\linewidth]{figures/scenario-heat-mitigation-maps.png}
    % \begin{subfigure}{\linewidth}
    %   \includegraphics[width=\textwidth]{figures/scenarios-prop-lulc.png}
    % \end{subfigure}
    % \begin{subfigure}{\linewidth}
    %   \includegraphics[width=\textwidth]{figures/scenarios-prop-T.png}  
    % \end{subfigure}
    % \begin{subfigure}{\linewidth}
    %   \includegraphics[width=\textwidth]{figures/scenarios-prop-mitigation.png}
    % \end{subfigure}
    % \captionsetup{width=\linewidth, margin={0cm,-.4\textwidth}}
    \caption{\label{fig:scenario-maps} Simulated LULC (top), temperature (middle) and heat mitigation (bottom) maps by transforming a 25, 50, 75 and 100\% of the candidate pixels to its corresponding LULC code with high tree canopy cover. The pixel values of each map are aggregated out of all the sampling approaches and simulation runs, i.e., the LULC maps show the mode, whereas the temperature and heat mitigation maps show the average. The axes tick labels display the Swiss CH1903+/LV95 coordinates. See the Jupyter Notebook at \hyperref[sec:si-scenarios]{section S2.1} for the detailed numbers of the figure.}
  \end{adjustwidth}
\end{figure}
When changing a 25, 50, 75 and 100\% of the candidate pixels, the maximum temperature $T$ for the reference date, i.e., 26.05$\degree C$, is progressively reduced to 25.77, 25.30, 24.82 and 24.49 $\degree C$ respectively, while the magnitude of maximum heat mitigation $T - T_{obs}$ increases from 0.49, 1.17, 1.81 and 2.22$\degree C$ respectively.
The largest heat mitigation magnitudes occur in the most urbanized parts, which are located along the main transportation axes.
The relationship between the proportion of candidate pixels transformed and the simulated distribution of air temperature can be approximated by a straight line with a negative slope (see \autoref{fig:si-scenario-T-regplot} and \autoref{fig:si-scenario-T-hists} for more details about this relationship).
% The strength of such a fit suggests that the constraints on the urban heat mitigation imposed by the existing urban fabric .

@@

% The differences between the spatially scattering or scattering the transformed pixels are most notable when considering the number of dwellers exposed to temperatures higher than 24$\degree$C and 25$\degree$C.
% Regarding the spatial configurations, scattering the transformed pixels instead of clustering them with other high tree canopy pixels can result in a reduction of the 3238, 9597 and 15323 dwellers exposed to temperatures higher than 24$\degree$C for the same proportions of transformed pixels of 25, 50 and 75\%, which respectively represents a 1.17, 3.47 and 5.53\% of the total number of dwellers. For temperatures higher than 25$\degree$C, the analogous reduction is of 20708 and 22748 dwellers when transforming a 25 and 50\% of the pixels, which represents a 7.48 and 8.22\% of the population.
The way in which the transformed pixels are sampled has significant effects on the human exposure to high temperatures (\autoref{fig:human-exposure-comparison}). 
\begin{figure}[ht]
  \begin{adjustwidth}{-.4\textwidth}{0cm}  
    \centering
    \includegraphics[width=\linewidth]{figures/human-exposure-comparison}
    \caption{\label{fig:human-exposure-comparison} Effect of the sampling approach on the population exposed to temperatures higher than 21, 22, 23, 24, 25 and 26$\degree$C for an overall proportion of transformed pixels of 0, 25, 50 and 75\%. The lines at the top of the bars represent the 95\% confidence intervals. The bar heights and the confidence intervals are computed out of all the simulation runs. See the Jupyter Notebook at \hyperref[sec:si-human-exposure]{section S2.3} for the detailed numbers of the figure.}
  \end{adjustwidth}
\end{figure}
Overall, scattering the transformed pixels to avoid forming a continuous tree canopy appears as the most effective approach to reduce the human exposure to the highest temperatures, followed by random sampling.
When transforming a 25 and 50\% of the candidate pixels with the scattering approach, the number of dwellers exposed to temperatures over 25$\degree$C diminishes from 124073 to 65108 and 4498 respectively. % (which is 4.57 an 64.57\% larger than the corresponding reduction when averaged among the three approaches)
Such a reduction is larger than its random sampling counterpart by 3125 and 8223 dwellers respectively, and larger than its clustering approach counterpart by 9359 and 21388 dwellers respectively.
% which is larger than its counterpart when reduction  corresponds to  less dwellers than when transforming the same amount of pixels with random sampling approach, and 9359 and 21388.

@@

\begin{figure}[H]
  \centering
  \includegraphics[width=.98\textwidth]{figures/monitoring-stations}
  \caption{\label{fig:monitoring-stations} Locations of the monitoring stations used to get the $T_{ref}$ and $UHI_{max}$ parameters. The axes tick labels display the Swiss CH1903+/LV95 coordinates. The basemap tile is provided by StamenDesign, under CC BY 3.0, with data from OpenStreetMap, under ODbL.}
\end{figure}
